EGGs are adhesive!

### 2025-03-11 calco/main.tex
lemma

\begin{restatable}{lemma}{kpp}\label{lemma:kern_pairs_pres_pullbacks}
	Let $f\colon X \to Y$ and $g\colon Z \to W$ be two arrows admitting kernel pairs and suppose that the solid part of the three squares below is given. 
	%
	If the leftmost square is commutative, then there is a a unique arrow $k_h: K_f \to K_g$ making the other two commutative
	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z}\]

		Moreover, it holds
		\begin{enumerate}
			\item if the leftmost square is a pullback, then also the other two are so;
			\item if $h$ is mono then $k_h$ is mono too.
		\end{enumerate} 
\end{restatable}
%[Proof in \Cref{kpp-proof}]

@@

	\begin{example} 
		We can consider the following four graphs with equivalence:
		\[\begin{split}
		\mathcal{G}_1&=(\emptyset, \emptyset, \emptyset, \id{\emptyset^\star}, \id{\emptyset^\star}, \id{\emptyset})\\
		\mathcal{G}_3&=(\emptyset, 2, 2, ?_{2^\star}, ?_{2^\star}, \id{2})
		\end{split} \qquad \begin{split}
		\mathcal{G}_2&=(\emptyset, 2, 1, ?_{2^\star}, ?_{2^\star}, !_2)\\
		\qquad \mathcal{G}_4&=(\emptyset, 4, 3, ?_{4^\star}, ?_{4^\star}, \pi)
		\end{split}\]
		where $\pi\colon 4\to 3$ is defined as
		\[0\mapsto 0 \quad 1\mapsto 0 \quad 2\mapsto 1 \quad 3\mapsto 2 \]

		Now, we have morphisms $h\colon \mathcal{G}_1\to \mathcal{G}_2$, $k\colon \mathcal{G}_1\to \mathcal{G}_3$, $z\colon \mathcal{G}_2\to \mathcal{G}_4$, $p\colon \mathcal{G}_3\to \mathcal{G}_4$ defined as:
		\[
		h:=(\id{\emptyset}, ?_2, ?_1)\quad k:=(\id{\emptyset}, ?_2, ?_2)
		\quad 
		z:=(\id{\emptyset}, j, z_Q)\quad p:=(\id{\emptyset}, j', p_Q)
		\]
		where 
		\[\begin{matrix}
			j\colon 2\to 4 & \begin{matrix}
			0\mapsto 0\\
			1  \mapsto 1
			\end{matrix} & z_Q\colon 1\to 3 &0\mapsto 0 & j'\colon 2\to 4 &\begin{matrix}0 \mapsto 2\\
			1 \mapsto 3
			\end{matrix} & p_Q\colon 2\to 3  &\begin{matrix}
		0\mapsto 1\\
		1\mapsto 2
			\end{matrix}
		\end{matrix} \]

		Notice that  $\pi\circ j=z_Q$ and$\pi\circ j'=p_Q$  Thus in this way $(\mathcal{G}_4, \{z, p\})$ becomes a pushout for $h$ along $k$.

		Let now $a$

		Un controesempio:
		Consideriamo i grafi senza edge e con nodi dati dal seguente cubo in cui le facce verticali sono pb e le due orizzontali sono po (tutte le frecce sono inclusioni)
		\[
	\xymatrix@C=10pt@R=10pt{&\emptyset \ar[dd]|\hole_(.65){\id{\emptyset}}\ar@{>->}[rr]^{?_2} \ar[dl]_{?_1} && 2 \ar[dd]^{\id{2}} \ar[dl]_{i_{2,3}} \\ 1  \ar[dd]_{i_{1,2}}\ar@{>->}[rr]^(.7){i_{1,3}} & & 3 \ar[dd]_(.3){i_{3,4}}\\&\emptyset \ar@{>->}[rr]|\hole^(.65){?_2} \ar@{>->}[dl]^{?_2} && 2 \ar[dl]^{j} \\2 \ar@{>->}[rr]_{j'} & & 4 }
		\]

		Qui abbiamo $j'(0)=2, j'(1)=3$ e  $i_{1,3}(0)=2$
		Come quozienti consideriamo il seguente cubo

		\[
		\xymatrix@C=10pt@R=10pt{&\emptyset \ar[dd]|\hole_(.65){\id{\emptyset}}\ar@{>->}[rr]^{?_1} \ar[dl]_{?_1} && 1 \ar[dd]^{\id{1}} \ar[dl]_{i_{1,3}} \\ 1  \ar[dd]_{i_{1,2}}\ar@{>->}[rr]^(.7){i_{1,3}} & & 3 \ar[dd]_(.3){\id{3}}\\&\emptyset \ar@{>->}[rr]|\hole^(.65){?_2} \ar@{>->}[dl]^{?_1} && 1 \ar[dl]^{k} \\2 \ar@{>->}[rr]_{k'} & & 3 }
		\]

@@

\begin{example}
	Considet the following hypergaphs with equivalence:
	\[\mathcal{G}:=(\emptyset, 2, 2, ?_{2}, ?_2, \id{2}) \quad \mathcal{H}:=(\emptyset, 1,1, ?_{1}, ?_1, \id{1}) \quad \mathcal{G}'=(\emptyset, 2, 1, ?_{2}, ?_{2}, !_{2}) \]

There is a morphism $d:=(\id{\emptyset}, !_2, \id{1})\colon \mathcal{G}'\to \mathcal{H}$. We can then construct the cube aside, where the bottom face is a pushout and the vertical ones pullbacks.
	\[
\xymatrix@C=30pt@R=10pt{&\mathcal{G}_1'\ar[dd]|\hole_(.65){a}\ar[rr]^{h'} \ar[dl]_{k'} && \mathcal{G}_2' \ar[dd]^{b} \ar[dl]_{z'}  \\ 
	\mathcal{G}_3'  \ar[dd]_{c}\ar[rr]^(.7){p'} & & \mathcal{G}' \ar[dd]^(.3){d} \\
	&\mathcal{G}\ar[rr]|\hole^(.3){({\emptyset, !_{2}, !_2})} \ar[dl]_{\id{\mathcal{G}}} && \mathcal{H} \ar[dl]^{\id{\mathcal{H}}}  \\
	\mathcal{G} \ar[rr]_{({\emptyset, !_{2}, !_2})} & & \mathcal{H}  }
\]\todo{sposta di lato}

\todo{finisci}

@@

\kpp*
\begin{proof}\label{kpp-proof}
Computing, we have
\[g \circ h \circ \pi_f^1 =  t \circ f \circ \pi_f^1     =  t \circ f \circ \pi_f^2     =  g \circ h \circ \pi_f^2\]

Therefore the existence  and uniqueness of the wanted $k_h$ follows at once from the the universal property of $K_g$ as the pullback of $g$ along itself.

To prove the second half of the thesis, we can notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks.
\[\xymatrix{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g} &  K_f \ar[r]^{\pi^1_f} \ar[d]_{\pi^2_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g}\\
	X \ar[r]_{f}& Y \ar[r]_{t} & W & X \ar[r]_{f} & Y  \ar[r]_{t}& W}\]

But then the following ones are pullbacks too.
\[\xymatrix{	K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} & K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} \\
	X \ar[r]_{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]_{g} & W & X \ar[r]_{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]_{g} & W}\]

The thesis now follows again by \Cref{lem:pb1}.   
\end{proof}

@@

\begin{lemma}\label{lem:po_set}
	The following are true:
	\begin{enumerate}
		\item if $(P, \{p_i\}_{i\in I})$ is a coproduct, then for every arrow $f\colon 1\to P$ there is exactly one $k\in I$ and $f_k\colon 1\to P_k$ such that $f=p_k\circ f_k$;

		\parbox{11cm}{
		\item suppose that the square on the right is a pushout and let $\iota_{m}\colon E\mto B$ be the inclusion of the complement of the image of $m$, then $(D, \{n, h\circ \iota_m \})$ is a coproduct; in particular, $h\circ \iota_f$ is mono.}\hfill \parbox{2cm}{\xymatrix@R=15pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}}
	\end{enumerate}
\end{lemma}
\begin{proof}
	\begin{enumerate}
		\item This is obvious.
		\item Let $f\colon E\to Z$ and $k\colon C\to Z$ be two arrows with the same codomain. . By definition of complement and since $m$ is mono we know that $(B, \{m, \iota_m\})$ is a coproduct. Define $\phi\colon B\to Z$ as the unique arrow such that \[\phi\circ m=k\circ g \qquad \phi \circ \iota_m=f\] 
		By construction there is a unique arrow $\psi \circ D\to Z$ such that 
		\[\psi \circ n=k \qquad \psi \circ h=\phi \]
		But this entails that 
		\[
		\psi \circ h\circ \iota_m =\phi \circ \iota_m=f\]

		On the other hand, if $\psi'\colon D\to Z$ is another arrow such that
		\[\psi' \circ n=k \qquad \psi' \circ h\circ \iota_m=f \]
		then we have
		\[\psi'\circ h\circ m=\psi'\circ n\circ g=k\circ g=\phi \circ m =\psi \circ h\circ n \]
		showing $\psi'=\psi$. \qedhere
	\end{enumerate}
\end{proof}

@@

\begin{lemma}\label{lem:nodim}
	Let $f,g\colon A\rightrightarrows B+C$ be two arrows with a coproduct as codomain. Then $(A, \{j_i\}_{i=0}^
	3)$ is a coproduct, where $j_i\colon A_i\mto A $ is defined by the following pullback squares.
	\[\xymatrix@C=30pt{A_0 \ar@{>->}[r]^{j_0}  \ar[d]_{p_0}& A   \ar[d]^{(f,g)}& A_1 \ar@{>->}[r]^{j_1}  \ar[d]_{p_1} & A \ar[d]^{(f,g)} \\
		B\times B \ar@{>->}[r]_-{i_B\times i_B} & (B+C)\times (B+C) & B\times C \ar@{>->}[r]_-{i_B\times i_C} & (B+C)\times (B+C)}\]
	\[ \xymatrix@C=30pt{A_2 \ar@{>->}[r]^{j_2}  \ar[d]_{p_2}& A   \ar[d]^{(f,g)}& A_3 \ar@{>->}[r]^{j_3}  \ar[d]_{p_3} & A \ar[d]^{(f,g)} \\
		C\times B \ar@{>->}[r]_-{i_C\times i_B} & (B+C)\times (B+C) & C\times C \ar@{>->}[r]_-{i_C\times i_C} & (B+C)\times (B+C)}\]
\end{lemma}

@@

	\noindent 
	\parbox{11.5cm}{\hspace{15pt}
	Let $\iota' \colon E'\mto C'$ and $\iota\colon E\to C$ be the inclusions of the complement of the images of of $m'$ and $m$ respectively . By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ and $(D, \{n, g\circ \iota\})$ are coproducts. We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]_{\iota} & C}}

@@

		\item  By \Cref{lem:nodim} we know that there exists $K_0$, $K_1$, $K_2$ and $K_3$ fitting in the following four pullback diagrams and such that $\{K_d, \{j_i\}_{i=0}^3\}$ is a coproduct.
		\[\xymatrix@C=45pt{K_0 \ar@{>->}[r]^{j_0}  \ar[d]_{(p_0, q_0)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
			B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota')} & D'\times D'}\]
		\[ \xymatrix@C=45pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
			E'\times B' \ar@{>->}[r]_-{(g'\circ \iota') \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D'}\]

	Now, if we compute we get
\begin{align*}
	n\circ b\circ p_0&= d\circ n'\circ p_0= d\circ \pi^1_d\circ j_0=d\circ \pi^2_d\circ j_0=d\circ n'\circ q_0=n\circ b\circ q_0\\
	g\circ c \circ  \iota' \circ p_3&=d\circ g' \circ  \iota' p_3=d\circ \pi^1_d\circ j_3=d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota' \circ q_3= g \circ c\circ \iota'\circ q_3
\end{align*}
Thus, since $n$ and $g$ are mono we get the dotted arrows in the diagram below.
\[\xymatrix{K_0 \ar@/^.3cm/[drr]^{p_0} \ar@{.>}[dr]^{\phi_0} \ar@/_.3cm/[ddr]_{q_0} &&& K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\ &K_b \ar[r]^{\pi^1_b} \ar[d]_{\pi^2_b}& B' \ar[d]^{b} & E' \ar[dr]_{\iota'}&K_c \ar[r]^{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & B' \ar[r]_{b} & B && C' \ar[r]_{c} & C }\]

Notice, moreover, that 
\[(\pi^1_d, \pi^2_d)\circ k_{g'}\circ \phi_3=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ \phi_3=(g'\times g')\circ (\iota'\circ p_3, \iota'\circ q_3)\]
and so $k_{g'}\circ \phi_3=j_3$.

Now, we also have
\begin{align*}
	n\circ b\circ p_1&=d\circ n'\circ p_1=d\circ \pi^1_d\circ j_1=d\circ \pi^2_d\circ j_1=d\circ g'\circ \iota'\circ q_1\\
	n\circ b\circ q_2 &=d\circ n'\circ p_2=d\circ\pi^2_D\circ j_2
	=d\circ \pi^1_d\circ j_2=d\circ g'\circ \iota'\circ p_2
\end{align*}

			Since the bottom face of the original cube is a pullback (again by \Cref{prop:regmono}), we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
			\[m\circ k_1=\iota'\circ q_1 \quad f\circ k_1=b\circ p_1 \quad m\circ k_2=\iota'\circ q_2 \quad f\circ k_2=b\circ q_2\]

			By \Cref{prop:isempty} we conclude that $K_1$ and $K_2$
 are both empty. In particular, we can also deduce that $(K_d, \{j_0, j_3\})$ is a coproduct.

@@

 On the other hand, notice that 
 \[\pi^1_{d}\circ k_{n'}\circ \phi_0=n'\circ \pi^1_b\circ \phi_0=n'\circ p_0=\pi^1_d\circ j_0 \qquad \pi^2_{d}\circ k_{n'}\circ \phi_0=n'\circ \pi^2_b\circ \phi_0=n'\circ p_0=\pi^2_d\circ j_0\]

 Thus $k_{n'}\circ \phi_0=j_0$ and we have
 \[(p_0, q_0)\circ \psi_0\circ \phi_0=(\pi^1_b, \pi^2_b)\circ \phi_0=(p_0, q_0)= \quad  j_0\circ \psi_0\circ \phi_0 = k_{n'}\circ \phi_0=j_0\]
We can conclude that $\phi_0$ is an isomorphism and that $k_{n'}$ is a coproduct injection.

 Furthermore, by definition of complement, $(C', \{\iota', m'\})$ is a coproduct. Applying again \Cref{lem:nodim} we can decompose $K_c$ in four parts, given by the pullbacks below:
 \[\xymatrix@C=45pt{H_0 \ar@{>->}[r]^{x_0}  \ar[d]_{(y_0, z_0)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_1 \ar@{>->}[r]^{x_1}  \ar[d]_{(y_1, z_1)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
 	A'\times A' \ar@{>->}[r]_-{m'\times m'} & C'\times C' & A'\times E' \ar@{>->}[r]_-{m'\times  \iota'} & C'\times C'}\]
 \[ \xymatrix@C=45pt{H_2 \ar@{>->}[r]^{x_2}  \ar[d]_{(y_2, z_2)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_3 \ar@{>->}[r]^{x_3}  \ar[d]_{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
 	E'\times A' \ar@{>->}[r]_-{\iota' \times m'} & C'\times C' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]

>>>>

\begin{restatable}{lemma}{kpp}\label{lemma:kern_pairs_pres_pullbacks}
	Let $f\colon X \to Y$ and $g\colon Z \to W$ be two arrows admitting kernel pairs and suppose that the solid part of the three squares below is given. 
	%
	If the leftmost square is commutative, then there is a a unique arrow $k_h\colon K_f \to K_g$ making the other three commutative.
	\[\xymatrix@R=15pt{X \ar[r]^{h}\ar[d]_{f}& Z \ar[d]^{g} & K_f \ar@{.>}[r]^{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]^{\pi^1_g} & K_f  \ar@{.>}[r]^{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}& K_f  \ar@{.>}[r]^{k_h} \ar[d]_{(\pi^1_f,\pi^2_f)} & K_g \ar[d]^{(\pi^1_g, \pi^2_g)}\\ Y \ar[r]_t& W & X \ar[r]_{h} & Z & X\ar[r]_{h} &Z & X\times X \ar[r]_{h\times h}& X\times Z}\]

		Moreover, the following hold true:
		\begin{enumerate}
			\item if $h$ is mono then $k_h$ is mono too;
			\item if the leftmost square is a pullback, then also the central too are so;
			\item if $h$ is mono and the first square is a pullback then the last one is a pullback too.
		\end{enumerate} 
\end{restatable}
%[Proof in \Cref{kpp-proof}]

@@

@@

	\todo{Qua va l'esempio di Fabio}
\end{example}

@@

\kpp*
\begin{proof}\label{kpp-proof}\begin{enumerate}
		\item Let $a,b\colon T\rightrightarrows K_f$ be two arrows such that $k_h\circ a=k_h\circ b$, then we have
\begin{align*}h\circ \pi^1_f\circ a&=\pi^1_g\circ k_h\circ a=\pi^1_g\circ k_h\circ b=h\circ \pi^1_f\circ b\\
	h\circ \pi^2_f\circ a&=\pi^2_g\circ k_h\circ a=\pi^2_g\circ k_h\circ b=h\circ \pi^2_f\circ b
\end{align*}
Since $h$ is mono this entails that
\[pi^1_f\circ a=pi^1_f\circ b \qquad pi^2_f\circ a=\pi^2_f\circ b\]
and thus $a$ must coincide with $b$.

 		\item  We begin by computing to get:
		\[g \circ h \circ \pi_f^1 =  t \circ f \circ \pi_f^1     =  t \circ f \circ \pi_f^2     =  g \circ h \circ \pi_f^2\]
		so that  existence  and uniqueness of the wanted $k_h$ follow at once from the the universal property of $K_g$ as the pullback of $g$ along itself.

		To prove the second half of the thesis, we can notice that, by \Cref{lem:pb1},  two rectangles below are pullbacks.
		\[\xymatrix@R=15pt{K_f \ar[r]^{\pi^2_f} \ar[d]_{\pi^1_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g} &  K_f \ar[r]^{\pi^1_f} \ar[d]_{\pi^2_f} & X \ar[r]^{h} \ar[d]_{f} & Z \ar[d]^{g}\\
			X \ar[r]_{f}& Y \ar[r]_{t} & W & X \ar[r]_{f} & Y  \ar[r]_{t}& W}\]

		But then the following ones are pullbacks too.
		\[\xymatrix@R=15pt{	K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} & K_f  \ar@/^.4cm/[rr]^{h\circ\pi^2_f}\ar[r]_{k_h} \ar[d]_{\pi^1_f}& K_g \ar[d]_{\pi^1_g}  \ar[r]_{\pi^2_g}& Z \ar[d]_{g} \\
			X \ar[r]^{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]^{g} & W & X \ar[r]^{h} \ar@/_.4cm/[rr]_{t\circ f}& Y \ar[r]^{g} & W}\]

		Thus the left halves of the rectangle above are pullbacks again by \Cref{lem:pb1}.

		\item 		For the last square, let $(t_1, t_2)\colon T\to X\times X$ and $s\colon T\to K_g$ be two arrows such that
		\[(\pi^1_g, \pi^2_g)\circ s=(h\times h)\circ (t_1, t_2)\]

		Thus there exist two arrows $x, y\colon T\rightrightarrows K_f$ fitting in the diagrams below.
		\[\xymatrix@R=15pt{T\ar@{.>}[r]_-{x} \ar@/^.3cm/[rr]^{s} \ar@/_.3cm/[dr]_{t_1}& K_f \ar@{->}[r]_{k_h} \ar[d]_{\pi^1_f} & K_g \ar[d]^{\pi^1_g} & T \ar@{.>}[r]_-{y} \ar@/^.3cm/[rr]^{s} \ar@/_.3cm/[dr]_{t_2} & K_f  \ar@{->}[r]_{k_h} \ar[d]_{\pi^2_f}& K_g \ar[d]^{\pi^2_g}\\ & X \ar@{>->}[r]_{h} & Y &&X \ar@{>->}[r]_{h}& Y} \]
		By the first point $k_h$ is mono, thus we can deduce that $x=y$. By construction we have
		\[(\pi^1_f, \pi^2_f)\circ x=(t_1, t_2) \qquad k_h\circ x=s\]

		Uniqueness follows now at once again from the fact that $k_h$ is mono.
		\qedhere

	\end{enumerate}

@@

\noindent 
		\parbox{11.7cm}{
\begin{lemma}\label{lem:po_set}
Suppose that the square aside is a pushout, with $m\colon A\mto B$ an injection. Let $\iota_{m}\colon E\mto B$ be the inclusion of the complement of the image of $m$. Then $(D, \{n, h\circ \iota_m \})$ is a coproduct. In particular, $h\circ \iota_m$ is mono.
\end{lemma}}\hfill \parbox{2cm}{\vspace{0cm}\xymatrix@R=15pt{A \ar@{>->}[r]^{m}  \ar[d]_{g}& B \ar[d]^{h}\\ C \ar@{>->}[r]_{n} & D}}
\begin{proof}
		 Let $f\colon E\to Z$ and $k\colon C\to Z$ be two arrows with the same codomain. By definition of complement and since $m$ is mono we know that $(B, \{m, \iota_m\})$ is a coproduct. Define $\phi\colon B\to Z$ as the unique arrow such that \[\phi\circ m=k\circ g \qquad \phi \circ \iota_m=f\] 
		By construction there is a unique arrow $\psi \colon D\to Z$ such that $\psi \circ n=k$ and $\psi \circ h=\phi$, thus 
		\[
		\psi \circ h\circ \iota_m =\phi \circ \iota_m=f\]

We are left with uniqueness. Let $\psi'\colon D\to Z$ be another arrow such that $\psi' \circ n=k$ and $\psi' \circ h\circ \iota_m=f$. Then we have
		\[\psi'\circ h\circ m=\psi'\circ n\circ g=k\circ g=\phi \circ m =\psi \circ h\circ m \]
		Hence $\psi'\circ h=\psi \circ h$ and so $\psi'=\psi$ because $(B, \{m, h\circ\iota_m \})$ is a coproduct. 
\end{proof}

@@

\begin{lemma}\label{lem:nodim}
	Let $f,g\colon A\rightrightarrows B+C$ be two arrows with a coproduct as codomain. Then $(A, \{j_i\}_{i=0}^
	3)$ is a coproduct, where $j_i\colon A_i\mto A $ is defined by the following pullback squares.
	\[\xymatrix@C=30pt@R=15pt{A_0 \ar@{>->}[r]^{j_0}  \ar[d]_{p_0}& A   \ar[d]^{(f,g)}& A_1 \ar@{>->}[r]^{j_1}  \ar[d]_{p_1} & A \ar[d]^{(f,g)} \\
		B\times B \ar@{>->}[r]_-{i_B\times i_B} & (B+C)\times (B+C) & B\times C \ar@{>->}[r]_-{i_B\times i_C} & (B+C)\times (B+C)}\]
	\[ \xymatrix@C=30pt@R=15pt{A_2 \ar@{>->}[r]^{j_2}  \ar[d]_{p_2}& A   \ar[d]^{(f,g)}& A_3 \ar@{>->}[r]^{j_3}  \ar[d]_{p_3} & A \ar[d]^{(f,g)} \\
		C\times B \ar@{>->}[r]_-{i_C\times i_B} & (B+C)\times (B+C) & C\times C \ar@{>->}[r]_-{i_C\times i_C} & (B+C)\times (B+C)}\]
\end{lemma}

@@

	\noindent 
	\parbox{11.5cm}{\hspace{15pt}
	Let $\iota' \colon E'\mto C'$ and $\iota\colon E\to C$ be the inclusions of the complement of the images of of $m'$ and $m$ respectively . By \Cref{lem:po_set}, $(D', \{n', g'\circ \iota\})$ and $(D, \{n, g\circ \iota\})$ are coproducts. We can also notice that $c\circ \iota'$ factors through $E$, as shown by the square on the right.}\hfill \parbox{4cm}{\vspace{-5pt}\xymatrix@R=15pt{E' \ar@{.>}[d]_{w} \ar@{>->}[r]_{\iota'} & C' \ar[d]^{c}\\ E \ar@{>->}[r]^{\iota} & C}}

@@

		\item 	 By \Cref{lem:nodim}, the previous point and the third point of \Cref{lemma:kern_pairs_pres_pullbacks}, we can decompose $K_d$ as the coproduct of $K_b$ $K_1$, $K_2$ and $K_3$ with coprojections given by, respectively, $k_{n'}$ and $j_1$, $j_2$ and $j_3$, where these objects and arrows fit in the following four pullbacks.
		\[\xymatrix@C=45pt@R=15pt{K_b \ar@{>->}[r]^{k_{n'}}  \ar[d]_{(\pi^1_b, \pi^2_b)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_1 \ar@{>->}[r]^{j_1}  \ar[d]_{(p_1, q_1)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
			B'\times B' \ar@{>->}[r]_-{n'\times n'} & D'\times D' & B'\times E' \ar@{>->}[r]_-{n'\times (g'\circ \iota')} & D'\times D'}\]
		\[ \xymatrix@C=45pt@R=15pt{K_2 \ar@{>->}[r]^{j_2}  \ar[d]_{(p_2, q_2)}& K_d   \ar[d]^{(\pi^1_d, \pi^2_d)}& K_3 \ar@{>->}[r]^{j_3}  \ar[d]_{(p_3, q_3)} & K_d \ar[d]^{(\pi^1_d, \pi^2_d)} \\
			E'\times B' \ar@{>->}[r]_-{(g'\circ \iota') \times n'} & D'\times D' & E'\times E' \ar@{>->}[r]_-{(g'\circ \iota')\times (g'\circ \iota')} & D'\times D'}\]

Let us now examine $K_1$ and $K_2$. We have
\begin{align*}
	n\circ b\circ p_1&=d\circ n'\circ p_1=d\circ \pi^1_d\circ j_1=d\circ \pi^2_d\circ j_1=d\circ g'\circ \iota'\circ q_1\\
	n\circ b\circ q_2 &=d\circ n'\circ p_2=d\circ\pi^2_D\circ j_2
	=d\circ \pi^1_d\circ j_2=d\circ g'\circ \iota'\circ p_2
\end{align*}

Since the bottom face of the original cube is a pullback (by \Cref{prop:regmono}), we conclude that there exist arrows $k_1\colon  K_1\to A$ and $k_2\colon K_2\to A$ such that
\[m\circ k_1=\iota'\circ q_1 \quad f\circ k_1=b\circ p_1 \quad m\circ k_2=\iota'\circ q_2 \quad f\circ k_2=b\circ q_2\]

By \Cref{prop:isempty} we conclude that $K_1$ and $K_2$
are both empty. In particular, this implies that $(K_d, \{k_{n'}, j_3\})$ is a coproduct.

We focus now on $K_3$. Computing we get
	\begin{align*}
	&g\circ \iota \circ w\circ p_3=g\circ c\circ \iota'\circ p_3=d\circ g'\circ \iota'\circ p_3=d\circ \pi^1_d\circ j_3\\=&d\circ \pi^2_d\circ j_3=d\circ g'\circ \iota' \circ q_3=g\circ c\circ \iota'\circ q_3=g\circ \iota \circ w\circ q_3
	\end{align*}

\noindent 
\parbox{3cm}{\xymatrix@R=15pt{ K_3 \ar[r]^{p_3} \ar@{.>}[dr]^{\phi_3} \ar[d]_{q_3}& E' \ar[dr]^{\iota'} \\E' \ar[dr]_{\iota'}&K_c \ar[r]^{\pi^1_c} \ar[d]_{\pi^2_c} & C'  \ar[d]^{c}\\ & C' \ar[r]_{c} & C }}\hfill\parbox{9.5cm}{By \Cref{lem:po_set} $g\circ \iota$ is a monomorphism, thus $w\circ p_3=w\circ q_3$ and therefore:
\[c\circ \iota'\circ p_3=\iota\circ w\circ p_3=\iota \circ w\circ q_3=c\circ \iota'\circ q_3\]
Thus we get the dotted $\phi_3\colon K_3\to K_c$ in the diagram aside.}

Moreover, $k_{g'}\circ \phi_3=j_3$ as shown by the following computation.
\begin{align*}
&(\pi^1_d, \pi^2_d)\circ k_{g'}\circ \phi_3=(g'\times g')\circ (\pi^1_c, \pi^2_c)\circ \phi_3=(g'\times g')\circ (\iota'\circ p_3, \iota'\circ q_3)\\=&((g'\circ \iota') \times (g'\circ \iota'))\circ (p_3, q_3)=(\pi^1_d, \pi^2_d)\circ j_3
\end{align*}

 \commentato{

@@

 On the other hand, notice that 
 \begin{align*}
 \pi^1_{d}\circ k_{n'}\circ \phi_0&=n'\circ \pi^1_b\circ \phi_0=n'\circ p_0=\pi^1_d\circ j_0 \\
 \pi^2_{d}\circ k_{n'}\circ \phi_0&=n'\circ \pi^2_b\circ \phi_0=n'\circ p_0=\pi^2_d\circ j_0
 \end{align*}

  Thus $k_{n'}\circ \phi_0=j_0$ and we have
 \[(p_0, q_0)\circ \psi_0\circ \phi_0=(\pi^1_b, \pi^2_b)\circ \phi_0=(p_0, q_0) \qquad  j_0\circ \psi_0\circ \phi_0 = k_{n'}\circ \phi_0=j_0\]
We can conclude that $\phi_0$ is an isomorphism, $(K_b, \{k_{n'}, (\pi^1_b, \pi^2_b)\})$ is a pullback for $(\pi^1_d, \pi^2_d)$ along $n'\times n'$ and  that$(K_d, \{k_{n'}, j_3\})$ is a coproduct.}

By definition of complement, we also know that $(C', \{\iota', m'\})$ is a coproduct. We can then apply again \Cref{lem:nodim}, decomposing $K_c$ in four parts, given by the pullbacks below:
 \[\xymatrix@C=45pt@R=15pt{H_0 \ar@{>->}[r]^{x_0}  \ar[d]_{(y_0, z_0)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_1 \ar@{>->}[r]^{x_1}  \ar[d]_{(y_1, z_1)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
 	A'\times A' \ar@{>->}[r]_-{m'\times m'} & C'\times C' & A'\times E' \ar@{>->}[r]_-{m'\times  \iota'} & C'\times C'}\]
 \[ \xymatrix@C=45pt@R=15pt{H_2 \ar@{>->}[r]^{x_2}  \ar[d]_{(y_2, z_2)}& K_c   \ar[d]^{(\pi^1_c, \pi^2_c)}& H_3 \ar@{>->}[r]^{x_3}  \ar[d]_{(y_3, z_3)} & K_c \ar[d]^{(\pi^1_c, \pi^2_c)} \\
 	E'\times A' \ar@{>->}[r]_-{\iota' \times m'} & C'\times C' & E'\times E' \ar@{>->}[r]_-{ \iota'\times  \iota'} & C'\times C'}\]
